\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in \red{Section XXX}. The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is. Pressure differences acting on the interface produces a net pressure force,

@@

%%%%%%%%%%%% 
\subsection{Model Validation}\label{section:results:validation}

@@

%%%%%%%%%%%%  
\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results:heleshaw}

>>>>

In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in Section \ref{section:results_homo_hete}. The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is. Pressure differences acting on the interface produces a net pressure force,

@@

%%%%%%%%%%%% 
\subsection{Model Validation}\label{section:results_validation}

@@

%%%%%%%%%%%%  
\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results_homo_hete}
